Predictions of Occupied Beds at Faculties Providing Daily Shelter And/Or Overnight Services Using Multivariate Linear Regression Implies That Modelling This Situation Using Other Models Would Be Better

### 2024-12-14 paper/paper.qmd
Fix some other minor mistakes, makes the test files for simulated and analysis data work

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false

# Load the necessary packages
library(tidyverse)
library(opendatatoronto)
library(janitor)
library(dplyr)
library(readr)
library(knitr)
library(kableExtra)
library(arrow)
library(ggplot2)
library(MASS)

@@

Packages used to complete the paper and/or the scripts include ggplot2 (@ggplot2), tidyverse (@tidyverse), opendatatoronto (@opendatatoronto), janitor (@janitor), dplyr (@dplyr), readr (@readr), knitr (@knitr), kableExtra (@kableExtra), arrow (@arrow), testthat (@testthat), car (@car), knitr (@knitr) and MASS (@MASS).

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
#| 
# Download the packages if necessary. If packages are already 
# downloaded, comment out the following lines.
install.packages("tidyverse")
install.packages("opendatatoronto")
install.packages("janitor")
install.packages("dplyr")
install.packages("readr")
install.packages("knitr")
install.packages("kableExtra")
install.packages("arrow")
install.packages("ggplot2")
install.packages("MASS")
install.packages("here")

# Load the packages
library(tidyverse)
library(opendatatoronto)
library(janitor)
library(dplyr)
library(readr)
library(knitr)
library(kableExtra)
library(arrow)
library(ggplot2)
library(MASS)
library(here)

@@

Packages used to complete the paper and/or the scripts include ggplot2 (@ggplot2), tidyverse (@tidyverse), opendatatoronto (@opendatatoronto), janitor (@janitor), dplyr (@dplyr), readr (@readr), knitr (@knitr), kableExtra (@kableExtra), arrow (@arrow), testthat (@testthat), car (@car), here (@here), and MASS (@MASS).
